---
title: "testing"
author: "Tim"
date: "February 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
```

```{r, echo=FALSE}
source('ensemble_functions.R') 
```

## Ensemble of Random Forests

Idea: Norm/stan transform data by column and fit an rf model. Then norm/stan transform by row and fit another model. Test

```{r}
library(tidyverse)
library(recipes)
library(caret)
library(rsample)
library(purrr)

library(doMC)
registerDoMC(cores = 4)

set.seed(123)
seeds <- vector(mode = "list", length = 11)

for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 4)
seeds[[11]] <- sample.int(1000, 1)

```
```{r}
train_data <- read_csv('../../train.csv')
test_data <- read_csv('../../test.csv')
```

Splits for testing:
```{r}
split <- initial_split(train_data, prop = 0.7)
train_data <- training(split)
test_data <- testing(split)
```

## Transformations

```{r}
recipe_list <- list(scale = scaled, corr = corred, row_scale = row_scaled)
cookbook <- map(recipe_list, ~.(train_data, test_data)) 
```

## Control

```{r}
control <- trainControl(
  method = "cv", 
  number = 10, 
  savePredictions = 'final',
  returnResamp = 'final',
  classProbs = TRUE,
  seeds = seeds)
```

## Train

```{r}
model_list <- map(
  cookbook,
  ~train(
    class ~ ., 
    data = .$training, 
    method = 'rf', 
    trControl = control)
)
```

```{r}
length(model_list)
names(model_list)
```

## Per Model CV Results

```{r}
results <- resamples(model_list)
summary(results)
```

```{r}
modelCor(results)
splom(results)
```

## Per Model Test Set Results

```{r}
matrices <- map2(
  model_list, 
  cookbook, 
  ~confusion_matrix(.x, .y$testing))

map(matrices, ~.[2:4])
```


## Ensemble Model

### Prediction out of fold ensemble

Shoutout to http://r4ds.had.co.nz/lists.html for nested lists
```{r}
pred_train <- oof_grab(model_list, train_data = map(cookbook, "training"))
pred_test <- oof_grab(model_list, test_data = map(cookbook, "testing")) 
```

```{r}
pred_ensemble <- train(
  class ~ .,
  data = pred_train,
  method = 'rf',
  trControl = control
)
```

```{r}
pred_ensemble
```

```{r}
confusion_matrix(pred_ensemble, pred_test)[2:4]
```

### Probability ensemble

```{r}
prob_train <- oof_grab(model_list, train_data = map(cookbook, "training"), type = 'prob')
prob_test <- oof_grab(model_list, test_data = map(cookbook, "testing"), type = 'prob') 
```

```{r}
prob_ensemble <- train(
  class ~ .,
  data = prob_train,
  method = 'rf',
  trControl = control
)
```

```{r}
prob_ensemble
```

```{r}
confusion_matrix(prob_ensemble, prob_test)[2:4]
```

## C5.0 in 

Test with resample
```{r}
c50_model_list <- map(
  cookbook,
  ~train(
    class ~ ., 
    data = .$training, 
    method = 'C5.0', 
    trControl = control)
)
```

```{r}
results <- resamples(c50_model_list)
summary(results)
modelCor(results)
```

```{r}
matrices <- map2(
  c50_model_list, 
  cookbook, 
  ~confusion_matrix(.x, .y$testing))

map(matrices, ~.[2:4])
```


## C5.0 Ensemble

```{r}
pred_train <- oof_grab(c50_model_list, train_data = map(cookbook, "training"))
pred_test <- oof_grab(c50_model_list, test_data = map(cookbook, "testing"))
```

```{r}
pred_ensemble <- train(
  class ~ .,
  data = pred_train,
  method = 'rf',
  trControl = control
)
```

```{r}
pred_ensemble
```

```{r}
confusion_matrix(pred_ensemble, pred_test)[2:4]
```

## rf to c50 corr

```{r}
names(c50_model_list) <- map_chr(names(c50_model_list), ~paste0("c50_", .))
names(model_list) <- map_chr(names(model_list), ~paste0("rf_", .))
```

```{r}
model_list <- append(model_list, c50_model_list)
```

```{r}
results <- resamples(model_list)
summary(results)
modelCor(results)
```

## rf c50 ensemble

```{r}
pred_train <- oof_grab(model_list, train_data = map(cookbook, "training"))

test_list <- append(map(cookbook, "testing"), map(cookbook, "testing"))
pred_test <- oof_grab(model_list, test_data = test_list)
```

```{r}
rf_c50_ensemble <- train(
  class ~ .,
  data = pred_train,
  method = 'rf',
  trControl = control
)
```

```{r}
rf_c50_ensemble 
```

```{r}
confusion_matrix(rf_c50_ensemble, pred_test)[2:4] 
```

```{r}
write_csv(data.frame(id = 1:63, class = predict(rf_c50_ensemble, pred_test)),
          'rf_c50_ensemble.csv')
```








